\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{amssymb}% http://ctan.org/pkg/amssymb
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%


 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }

\title{Unit 15}
\author{Chris}
\date{}

\begin{document}

\maketitle
\tableofcontents
\break


\section{P1}


\subsection{Lethal Company}
\subsubsection{purpose of a game}

The purpose of Lethal Company is to hunt for scrap so that you can sell it and make the quota with your friends. In Lethal Company quota increase every time you hit the quota. So to hit the new quota goals you will have to go to more harder and difficult moons.

\subsubsection{Audience of a game}

The Audience of Lethal Company is everyone. The game cost £8.50 so it has a very low barrier to entry making it really easy for anyone to play. Lethal company has had an all time peak of 239,369 players.

\subsubsection{Common features of a game}

The common feature in Lethal Company are the standard movement keys and picking up items with left click.

\subsubsection{First/third person}

Lethal Company has first person perspective. Having first person perspective makes the horror aspect of the game more scary because your more immersed into the game

\subsubsection{Player characters}

Lethal Company is coop games there is 1-4 playable characters.

\subsubsection{Non-player characters}

Lethal Company has multiple Non-player characters(NPC). This can depends on the moon the players is playing and what phase the moons is on, this defined by power and each NPC takes of certain amount of power this also depends on each moon.

\subsubsection{Sprites}

Lethal Company has no sprites.All of the games assets are 3D even the hud is 3D just flatten down to look 2D.By having all the assets 3D means that the developer has more flexibility when it comes to developing the future content

\subsubsection{Achievement attainment}

The Achievement attainment in Lethal Company is that the quota is constantly increasing by doing this is cause the game to constantly increasing "achievement" for the players involved 

\subsubsection{Player interaction/controls} 

Lethal Company has a fixed controller. The control layout is standard across the entire game, everyone has the same control layout which makes it easy for the teach new players the games. 


\break

\subsection{Minecraft}
\subsubsection{purpose of a game}

Minecraft is a media franchise developed from and centred around the video game of the same name. Primarily developed by Mojang Studios, the franchise consists of five video games, along with various books, merchandise, events, and an upcoming theatrical film. Microsoft acquired Mojang Studios in 2014, alongside the Minecraft franchise and its editions. 

\subsubsection{Audience of a game}

The Audience of Lethal Company is mainly younger people. The cost \$29.99 and is the most popular game of all time and it is a global phenom

\subsubsection{Common features of a game}

The common feature in Minecraft are the standard controller layout and movement. The movement in Minecraft is very ground it is hard to get away particular fast.

\subsubsection{First/third person}

Minecraft has first person perspective and third person perspective this is changed by pressing F5. 

\subsubsection{Player characters}

Minecraft can be played in single player or in multiplayer. Single player has only one player where as multiplier can have over 100 players in a server 

\subsubsection{Non-player characters}

Minecraft has multiple Non-player characters(NPC). There is are normally the monster eg;creeper,zombie, enderman etc ... There is also friendly NPCs for example: pig,cow and villager.

\subsubsection{Sprites}

Minecraft has 2D sprites, these 2D are normally small 1 blocks objects for example flowers, signs and ladders

\subsubsection{Achievement attainment}

The achievements in Minecraft are called advancements. Minecraft rewards the player for progressing in the game, these advancements can be for the creating items or opening your inventory etc... This helps keep the player engaged. There is 110 advancements in minecraft.

\subsubsection{Player interaction/controls} 

Minecraft has customisable controller inputs but the inputs that default are universal. The player has a lot of interactions in the game for example crafting weapons and tools in the crafting table or spawning in the enderdragon with endercrystals.

\break
\section{M1}

\subsection{Compare and contrast Lethal Company and Minecraft}


\begin{tabular}{ |p{5cm}|p{5cm}|p{5cm}| }
        \hline
                            & Lethal Company    & Minecraft \\
        \hline
        purpose of a game   & &#x2611;;     &  \cmark \\
        \hline
        audience of a game  & \cmark        & \xmark \\
        \hline  
        first person        & \cmark        & \cmark \\
        \hline
        third person        & \xmark             & \cmark \\
        \hline
        player characters   & \cmark        & \cmark \\
        \hline
        non-player characters & \cmark      & \cmark \\
        \hline
        sprites             & \xmark             & \cmark \\
        \hline
        achievement attainment & \xmark          & \cmark \\
        \hline
        maintaining a player’s interest & \cmark& \cmark \\
        \hline
        player immersion    & \cmark        & \cmark \\
        \hline
        progression         & \xmark            & \cmark \\
        \hline
        competition         & \cmark        & \xmark \\
        \hline
\end{tabular}
\break


There is not much similar about the two games, Minecraft is open world sandbox where as Lethal Company coop horror survival game. How ever there is coop in both games and have games have standard controller layouts. Minecraft and Lethal both do have an "endless" game where there is no need and you just get stronger and stronger.

Minecraft compared to Lethal Company is much more free gamer, this is because Minecraft is sandbox and the player choose what they do for example they create castle or pvp or go sight seeing etc.. . Where ass Lethal company decides what you do and how long you will be doing the only variable your are in control is how much scrap you can get because that is limited by the player not the game.





\break
\section{Sources}
\url{https://lethal-company.fandom.com/wiki/Lethal_Company_Wiki} \\
\url{https://en.wikipedia.org/wiki/Minecraft_(franchise)} \\
\url{https://minecraft.fandom.com/wiki/}

\end{document}
