\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\graphicspath{ {./images/} }
\usepackage[square,numbers]{natbib}
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
\usepackage{hyperref}

\bibliographystyle{dinat}


\begin{document}


\title{Unit 13}
\author{Chris Hadden}
\date{}
\maketitle

\section{P4 Legal and ethical restrictions on the use of social media as part of
digital marketing campaigns}

In Titanica Media we take great care in dealing with our legal obligations, because if we do not then there could be severe fines and we could even be disallowed from collecting social media data.
We will start this report by explaining what the exact legislation is that we need to work with

\section{Legislation}
\subsection{Data Protection Act 2018}
The Data Protection Act 2018 is a law in the UK that sets out how personal information should be handled to protect individuals' privacy. 
It builds aligns with the General Data Protection Regulation (GDPR) which is a comprehensive privacy regulation from the European Union.
It gives users of social media power over how their personal data is used and stored. 
The main concepts are
\begin{itemize}
    \item Personal Data Protection
    \item Control Over Personal Data
    \item Consent
    \item Transparency
    \item Data Use Limitation
    \item Data Protection Officers
    \item Penalties for Non-compliance
\end{itemize}

\bigskip

The main restrictions on our company that you need to be aware of are
\begin{itemize}
    \item Lawfulness, Fairness, and Transparency Data must be processed lawfully, fairly, and in a transparent manner. This means we must have a valid basis and user consent for processing personal data and must clearly inform individuals about how their data is used.    
    \item Purpose Limitation. We can only collect personal data for specified, explicit, and legitimate purposes.
    \item Data Minimization. We should only collect personal data that is necessary for the purposes for which it is processed.
    \item Accuracy. Personal data must be accurate and, where necessary, kept up to date.
    \item Storage Limitation. Personal data should be kept in a form that permits identification of data subjects for no longer than is necessary.
    \item Integrity and Confidentiality. Personal data must be processed in a manner that ensures appropriate security of the data.
    \item Accountability. We are responsible for compliance with the principles outlined above. This includes keeping records of data processing activities.
    \item Data Protection Officers. Poppy is our Data Protection Officer (DPO). You need to let her know about any data collection operations you are doing.
\end{itemize}

\subsection{Copyright, Designs and Patents Act 1988}
The Copyright, Designs and Patents Act 1988 is a UK law that provides protection for creators of original works, such as writers, artists, and inventors.

It's main points are
\begin{itemize}
    \item Copyright. The law protects original works of authorship, including literary, dramatic, musical, and artistic works, plus sound recordings and films. It gives creators exclusive rights to use, reproduce, and distribute their works. 
    \item Designs. This protects the visual appearance or aesthetics of a product, provided the design is new and has individual character.
    \item Patents. Patents protect new inventions, allowing inventors exclusive rights to make, use, sell, and import their invention. 

\end{itemize}

What this means for Titanica Media is that we cannot use copyrighted works, designs or patents without permission from the copyright holder, which may involve licensing agreements.


\subsection{The Privacy and Electronic Communications (EC Directive) Regulations 2003}

The Privacy and Electronic Communications Regulations (PECR), are regulations that focus primarily on protecting personal privacy in electronic communications.

It's main points are
\begin{itemize}
    \item Cookies and Similar Technologies. We must inform users about any cookies or  technologies that track information about users on websites. Users must also give their consent before these cookies can be used.
    \item Marketing Communications. PECR restricts sending electronic marketing messages without the recipient's prior consent.
    \item Security of Services. We must ensure that their services have adequate security measures to protect users' data from being accessed or altered without authorization.
    \item Traffic and Location Data. PECR requires companies to keep any data that can track users' locations confidential, unless users have given consent for their data to be used.
\end{itemize}

For us this means that we need to ensure that we have users consent anytime we deal with their data or contact them. If you have any questions then ask Poppy.

\newpage
\section{Business policy and practice}
We have various predefined policies that will help out in these areas of legislation. Poppy has copies of them all for you to use.

\subsection{Acceptable Use}
This outlines the rules and guidelines for using the systems and data of Titanica Media.
It has a \textbf{Purpose} and \textbf{Scope} that outlines why they exist and who it applies to.
It describes what \textbf{Legal} compliance we are bound to. Importantly it defines \textbf{Data Access} and what use we make of it.

\subsection{Social Media}
This policy is important for ensuring that the use of social media aligns with the our values and protects our reputation.
Again, it has a \textbf{Purpose} and \textbf{Scope} that outlines why they exist.
It outlines everyone \textbf{Responsibilities} in terms of accessing social media data and describes any \textbf{Prohibited Behavior}

\subsection{Recruitment Use}
This policy exists to make sure that our hiring practices are fair, transparent, and legally compliant.
It also has a \textbf{Purpose} and \textbf{Scope} that outlines why they exist.
It defines the \textbf{Recruitment Process} making sure there is no bias or requesting of personal information.
It ensures \textbf{Equality and Non-Discrimination} in the process and it ensures \textbf{Confidentiality and Security}
 

\subsection{Your responsibilities}
All these polices enforce our Ethical standpoint on user data and it's use. While we can make money for the company by selling on data, we typically do not do that and if we do then we have to comply with all legislation and have to get sign off from Poppy.

By way of an example, if we do not comply then we could loose reputation and get fined like Meta recently was

In May last year Ireland's Data Protection Commission (DPC) investigated Meta Platform Ireland Limited ("Meta Ireland"). They fined the company €1.2 billion for not following proper privacy rules. The DPC said Meta Ireland sent personal data from Europe to the US without making sure it was kept private, which was against the rules while they were running their Facebook services. \cite{Meta}
\bibliography{bibliography}

\end{document}

