\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

\begin{document}


\title{Unit 8 Learning Outcomes}
\author{Chris Hadden}
\date{}
\maketitle

\section{D1 Assess the impact of digital marketing on an identified product}

We are going to assess some real life marketing campaigns and try to assess where they succeeded or where they failed.


\begin{table}[h!]
    \centering
    \begin{tabular}{|c|c|}
       \hline
       \multicolumn{1}{c}{\bfseries Company Name} & \multicolumn{1}{c}{\bfseries What was positive about it?}  \\
             \hline
         Yooo & test \\
        \hline
    \end{tabular}

\end{table}

For this task, you are required to create a written report on the impact of digital marketing on an identified
product. You will carry out research into a digital marketing campaign and the impact that the campaign had
on the identified product, assessing the impact whether it be positive, negative or a mixture of both.


Assess - Offer a reasoned judgement of the standard/quality of situation/skills informed by relevant facts.
For this final task, you will choose a “real life” product / brand / organisation and assess the impact of this
campaign, therefore, you could refer back to the research you did into digital campaigns in the lesson on positive
and negative (successful and failed) digital marketing campaigns.
Your report should include the following:
o Report Title – e.g. Assessment of the impact of digital marketing on an identified product
o An introduction, outlining what you have been asked to report on (i.e. you have been asked to
assess the impact of digital marketing on an identified product).
o Then, you should go on to explain the digital marketing campaign you have researched, explaining
the following:
 What were the goals of the campaign?
 What channels were used?
 Who was the target audience?
 How much did it cost? (NB: don’t worry if you cannot find this information)
 What were the end results?
The following should be considered in your explanation:
- The role of marketing within business (Market research, raising awareness and affecting perception of
need via promotion and advertising, selling)
- Digital marketing as a business tool (Business establishment, business growth, business continuity)
- Strategies towards identified marketing goals (Identifying customers/markets, raising awareness,
increase sales, gaining information, gathering data and creating traffic)
o You will then need to assess the impact of the campaign – i.e. was the campaign successful or
not? You need to:
 Explain, in detail, what worked, what didn’t, feedback by the end user (where relevant),
what lessons could be/were learned.
o Conclusion/Summary


References:
These should be extensive! For images and any websites you have used for research, collect as you go, so
that you don’t have to go back and search for them later. Also, don’t forget to reference the Student
Textbook as well any other books/websites you have used during your research.
continued on next page...

\end{document}

