\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{titlesec}
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }

\title{Unit 23}
\author{Chris}
\date{}

\begin{document}


\section{Title}
The business proposal for our development of the cognitive computing solutin is going to named 
Cognitive computer support aid for healthcare

\section{Table of Contents}
The table of contents of the work
\begin{enumerate}
	\item	Problem Solving
	\item	
\end{enumerate}

\section{The Problem Statement}
we are here to solved the problem in health care of patients being unable to get support for their needs quickly and effiently.

\section{The Proposed Solution}
The plan to solve this problem is going to use cognitive computing to have smart chatbots. Using chatbots will make it more easier for our end users to help them to identify their problems and hopefully be able to hand them off to a actual doctor. By doing this it will speed up the process of diagnosing our patiend hopefully leading them to have a better life.

\section{Risk}
The risk in doing this are that might misdiagnose our patiens since it is a robot talking to them so that is why we have them talking to a doctor at the end of the talk with them. There could be a lost of jobs since our new system will be replacing their jobs but we see this a good since it will   . 
There is a potienal for social and mabey ethical issues since being diagnosed by a robot is a soulless and could make the customers feel to help with these concerns we have the 

\section{The Timeline}
The timeline of the project
\begin{enumerate}
	\item The Proposed start
	\item Precedence table
	\item Milestones
	\item Estimated finish date
	\item Date of acceptance 
	\item Gantt chart
\end{enumerate}

\subsection{The proposed start}
The proposed start will be on the 10th may 2024. What we plan to do when we begin we will start making our intial design mock ups for cognitive computer support air
The design documation will be made to show the postive and negatives of what having cognitive 

\subsection{Precedence table}
The 
Train chat bot

\subsection{Milestones}
The Milestone for our project will be 
	\begin{enumerate}
		\item Making the chatbot talk to the user
		\item Get the chatbot to diagnose the user
		\item Get the chatbot to work over the phone
		\item Make sure all these systems works together
		\item Public release
	\end{enumerate}

\subsection{Estimated finish date}

The finish dates is 10th May 2025. We exepct everything to be delivered and ready by that time so that our clients have a product available 

\subsection{Date of acceptance}
The date of acceptance will 

\subsection{Gantt chart}







\section{Costs}
The cost for this going to high since this is a large since this a cognitive computing 
Cost loads of money

\section{The Acceptance}
Acceptance of our project will be hard since replacing humans is hard job but the improvement to the health. The increase to health and efficiency.

\begin{enumerate}
    \item 
\end{enumerate}

\end{document}
